\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{enumitem}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=11in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.6cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheaing}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
%\hspace{0.5cm}\\[-0.2cm]

\begin{minipage}{0.5\linewidth}
\textbf{\Large Vighanesh Sharma}\\
\text{Master's of Science in Computers Science} (MSCS)\\
\text{B.Tech. in Computer Science and Engineering} (CSE)\\
\end{minipage}
&\hspace{2.5cm}
\begin{minipage}{0.5\linewidth}
\text{Email: vxs240002@utdallas.edu}\\
\text{Alt Email: vighaneshsharma@gmail.com}\\
\text{Contact No.: +91-9796466366} \\
\end{minipage}

\resheading{\textbf{EDUCATION} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}
\item \textbf{University of Texas} \hfill \emph{Dallas, Texas. August 2024 - present}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

Master's of Science in Computer Science (MS CS)

\item \textbf{Indian Institute of Technology (IIT)} \hfill \emph{Ropar. 2017-2021}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

Bachelor's of Technology in Computer Science and Engineering (B.Tech CSE)

\end{itemize}

\resheading{\textbf{SKILLS} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}[itemsep=0.1pt]

\item \noindent \textbf{Languages} : Python, Golang, C/C++, JavaScript, HTML, Intel x86-64, Java
\item \noindent \textbf{Software/Frameworks} : Kubernetes, Docker, Linux, Git, Grafana, Prometheus, Guacamole, BDD, Cucumber, REST, PostgreSQL, NoSQL, Flask, React
\end{itemize}

\resheading{\textbf{WORK EXPERIENCE} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}
\item \textbf{GE (General Electric) HealthCare} \hfill \emph{July 2021 - July 2024}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

Software Engineer (Edison HealthLink PaaS)
	\begin{itemize}\itemsep \isep
	\item Designed, built and enhanced \textbf{PaaS components} for EHL, a \textbf{platform} used to run applications in a high-availability cluster in the hospital environment. 
    \item Improved Connectivity Service \textbf{(Python/Flask Back-end)} used to connect remotely to machines in the infrastructure by \textbf{automating connections} to the VMs and enabling connection through \textbf{SSH Keys}. Addressed multiple bugs.
    \item Enhanced and improved \textbf{logging service} by adding functionality to feed logs through \textbf{REST API}, excluding logs, multiline logging etc.
    \item Maintained and improved Flair component which consisted of a \textbf{REST API} and an \textbf{AWS lambda} service written in \textbf{Go}; by \textbf{automating BDD tests} in \textbf{Gitlab Pipeline}, implementing \textbf{unit-tests} with \textbf{90+\% coverage}, Refactored and reduced the codebase size and addressed critical vulnerabilities. 
    \item Successfully completed multiple \textbf{Proof of Concepts (POCs)}, due to \textbf{architectural changes}.
	\end{itemize}

Software Engineer (EEDP Technical Leadership Program)
	\begin{itemize}\itemsep \isep
	\item Developed \textbf{micro-services} in \textbf{Go} and \textbf{Angular} to enable \textbf{Secure Access} for service users.
    \item Developed and maintained the \textbf{micro-services} for \textbf{RBAC} (Role Based Access Control) Software; Resolved numerous bugs, increased unit test coverage to 90\%, and addressed critical vulnerabilities.
	\item  Developed a \textbf{'System for Detecting breach using AI'} and filed patent for it.
	\end{itemize}
 
Software Intern (EID), \hfill \emph{June 2020 - August 2020}
	\begin{itemize}\itemsep \isep
	\item  Developed a Web Based CT Scan Viewer using \textbf{VTK.js, Cornerstone.js} and \textbf{HTML}.
	\end{itemize}
\end{itemize}

\resheading{\textbf{CERTIFICATION} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}
\item Advanced Certification Program on 'Digital Health and Imaging Technology'. I recieved an \textbf{A+}. 
\end{itemize}

\resheading{\textbf{ACHIEVEMENTS} }\\[\lsep]
\vspace{1.0pt}

\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item Secured a Rank of \textbf{2029, 99.8 Percentile} (out of 1 million candidates) in \textbf{JEE Advanced 2017} .
\item Got Recognised for going \textbf{Above and Beyond} at GEHealthCare for filing a \textbf{patent}.
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textbf{Visual Cryptography} - Studied and Implemented different \textbf{Visual Secret Sharing} Schemes and compiled all the results to implement \textbf{Coloured Visual Secret Sharing Scheme for General Access Structures in Python}. 	
\item \textbf{Spam SMS Filter in C Language} - Implemented a Spam SMS Filter in C Language.
\item \textbf{Interactive Portfolio} - Created personal portfolio in the style of a game web-app using \textbf{React, Phaser3} and \textbf{Tailwind CSS}. (\textbf{ vighaneshs.github.io} )
\item \textbf{x64 Assembly Simulator}
\item \textbf{Cryptanalysis} of different AES like Lightweight Cryptography Algorithms
\item Various \textbf{Game Projects} on \textbf{Unity3D}
\item Faculty Management System using \textbf{PostgreSQL, NoSQL(MongoDB) and NodeJS}.
\item A Game on FPGA
\end{itemize}

\resheading{\textbf{RELEVANT COURSES} }\\[\lsep]
\vspace{1.0pt}
\begin{itemize}[itemsep=0.1pt]
\item \noindent \textbf{Computer Science} : Data Structures and Algorithms, Operating Systems, Databases, Applied Cryptography, Computer Graphics, Networks, Software Engineering, Theory of Computation,  Algorithms and Design, Computer Architecture,
Programming Paradigms and Pragmatics, Digital Logic Design, Data Science.
\item \noindent \textbf{Mathematics} : Calculus, Probability and Statistics, Linear Algebra, Integral Transforms, Differential Equations.
\end{itemize}

\end{document}

